\huge A Usability Evaluation of Tor Launcher

### 2016-11-15 pets2017-paper/pets2017-paper.tex
fix chi squared numbers
add chi squared calculation into comments
Karsten's comments

Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination. 
Tor Browser~\cite{torbrowser} is a modified Firefox browser with a built-in Tor client that
is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface asks the user to configure
bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper). This is the object of our study.

@@

@@

Tor relays are routers in the Tor Network that receive and route Tor traffic. 
The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays that direct traffic to the destination.

@@

In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. (Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) Fig.~\ref{fig:topology} illustrates the interacting components.

@@

\subsection{Connecting to Tor} 
Configuring a bridge requires providing a
``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% were male. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instructions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

@@

\label{all-participant-edges} 
\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges}
\caption{
A summary of our valid participants' paths through the interface.
The length of the bars show the total time taken to complete the task,
except for those we cut off after approximately 40 minutes.
Different colors indicate which screen they were on during the experiment.
The ``not running'' times are those when Tor Launcher was closed (
i.e. searching for help in another browser, restarting the application, etc.).
}
\label{fig:all-participant-edges}
\end{figure*}

@@

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

@@

\section {Acknowledgments}
Many generous people helped us along the way. <Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours. <Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.  <Redacted>, and <redacted> provided me with insider insight into the design decisions made at Tor.
% Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.

>>>>

Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination. 
Tor Browser~\cite{torbrowser} is a modified Firefox browser with a built-in Tor client that
is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface (Figure~\ref{fig:old-interface}) asks the user to configure
bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper). This is the object of our study.

@@

We hope that our work contributes to Tor Browser and provides an interesting case study. We also encourage the use our evaluation pipeline and methods for evaluating other user-facing interfaces and features.

@@

 A user uses the Tor network to indirectly connect to websites using Tor Browser. The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.  Tor relays are the routers in the Tor Network. 
Guard relays that serve as an entry node into the Tor network and receive packets from the user. Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network. Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination.

@@

In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. This is to maintain consistency with the wording in the configuration interface. Fig.~\ref{fig:topology} illustrates the interacting components. We recognize that, a proxy is technically anything that acts as an intermediary between clients and servers. By this definition, a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy.

@@

\subsection{Connecting to Tor} 
Configuring a bridge requires providing a
``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:old-bridge-combobox}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% were male. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 3 heard of it but not used it, and the remaining 9 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instructions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

@@

\label{all-participant-edges} 
\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges}
\caption{
A summary of our valid participants' paths through the interface.
The length of the bars show the total time taken to complete the task,
except for those we cut off after approximately 40 minutes.
Different colors indicate which screen they were on during the experiment.
If participants were doing other things (i.e. searching for help in another browser)
while off-focus, this time still counts as spending time in that off-focus window. 
``Not running'' are times when Tor Launcher was closed (
i.e. restarting the application).
}
\label{fig:all-participant-edges}
\end{figure*}

@@

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

%using http://www.socscistatistics.com/tests/chisquare/Default2.aspx
% OLD VS NEW: The chi-square statistic is 2.8079. The p-value is .093802.
% E1-old vs E1-new: no valid calculation  since it's the exact same ratio (19 succeeded, 0 failed) 
% E2-old vs E2-new: The chi-square statistic is 3.0929. The p-value is .078636.
% E3-old vs e3-new: The chi-square statistic is 1.3666. The p-value is .242403.

@@

\section {Acknowledgments}
Many generous people helped us along the way. <Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours. <Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.  <Redacted> and <redacted> provided me with insider insight into the design decisions made at Tor.
% Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.
